\LARGE \bf Towards a Data-driven Approach to Motion Planning

### 2015-02-27 paper2015asml.tex
fixed reference to finger-tip/tool

{\bf Path length:}
%The length of the trajectory \tj{} computed as the sum over trajectory segments of the euclidean distance between end points of the segment, or
%\begin{equation}
%\text{Length} = \sum_{i=0}^{n-1} \| q_\text{i}-q_\text{i+1} \|
%\end{equation}
We compute path length for the joint-space trajectory and for three workspace trajectories for the elbow ($\xi_\text{elbow}$), wrist ($\xi_\text{wrist}$) and finger-tip ($\xi_\text{tip}$) links of the right arm (the moving arm). We also compute the length of the trajectory in angular distance by summing over the waypoints $\arccos( \langle Q_\text{i},Q_\text{i+1}\rangle^2-1 )$ where $Q_\text{i}$ is the quaternion orientation for the $i$-th waypoint (referred to later as the ``quat\_dist'' feature).

@@

Next, we compute comparison features between $\xi_{\text{BFS}}$ and three workspace trajectories for the elbow ($\xi_\text{elbow}$), wrist ($\xi_\text{wrist}$) and finger-tip ($\xi_\text{tip}$) links. The comparison features computed between each pair of trajectories are the Hausdorff distances~\cite{dubuisson1994modified} and Dynamic Time Warping~\cite{senin2008dynamic} distances. \hl{These features have also often been used for comparing trajectories in applications like location based services and are useful in comparing trajectories that might have different lengths or shapes.}~\cite{chen2013dynamic}.

>>>>

{\bf Path length:}
%The length of the trajectory \tj{} computed as the sum over trajectory segments of the euclidean distance between end points of the segment, or
%\begin{equation}
%\text{Length} = \sum_{i=0}^{n-1} \| q_\text{i}-q_\text{i+1} \|
%\end{equation}
We compute path length for the joint-space trajectory and for three workspace trajectories for the elbow ($\xi_\text{elbow}$), wrist ($\xi_\text{wrist}$) and finger-tip/tool ($\xi_\text{tip}$) links of the right arm (the moving arm). We also compute the length of the trajectory in angular distance by summing over the waypoints $\arccos( \langle Q_\text{i},Q_\text{i+1}\rangle^2-1 )$ where $Q_\text{i}$ is the quaternion orientation for the $i$-th waypoint (referred to later as the ``quat\_dist'' feature).

@@

Next, we compute comparison features between $\xi_{\text{BFS}}$ and three workspace trajectories for the elbow ($\xi_\text{elbow}$), wrist ($\xi_\text{wrist}$) and finger-tip/tool ($\xi_\text{tip}$) links. The comparison features computed between each pair of trajectories are the Hausdorff distances~\cite{dubuisson1994modified} and Dynamic Time Warping~\cite{senin2008dynamic} distances. \hl{These features have also often been used for comparing trajectories in applications like location based services and are useful in comparing trajectories that might have different lengths or shapes.}~\cite{chen2013dynamic}.
